---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggmouse)
```

# ggmouse

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/marcosci/ggmouse/branch/master/graph/badge.svg)](https://codecov.io/gh/marcosci/ggmouse?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/marcosci/ggmouse/workflows/R-CMD-check/badge.svg)](https://github.com/marcosci/ggmouse/actions)
<!-- badges: end -->

The goal of ggmouse is to ...

## Installation

###  Prerequisities

``` bash
brew install xdotool
defaults write org.x.X11 enable_test_extensions -boolean true  
defaults write org.macosforge.xquartz.X11 enable_test_extensions -bool yes   
```

###  Package 

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marcosci/ggmouse")
```

## Example

### Mouse movement tracking

If you use RStudio, the most convienent way to track your mouse movement with `ggmouse` is to use the jobs pane. Just create somewhere a file like the following:

```r 
library(ggmouse)

mouse_file <- tempfile(fileext = ".txt")
track_mouse("00h00m90s", mouse_file)

momove <- import_mouse(mouse_file)

visualize_mouse(momove, "tinygrid")
```

... and specify everything in there that is of interest to you. The time, maybe you don't want to save the coordinates in a tempfile or you don't want to immediately plot the data.

Then run the job with the following settings:

--- IMAGE ----

### Visualize mouse movement

```{r}
visualize_mouse(mouse_track, type = "dot")
```



## Code of Conduct

Please note that the ggmouse project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
